---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rtilities2

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!--[![CRAN status](https://www.r-pkg.org/badges/version/rtilities2)](https://CRAN.R-project.org/package=rtilities2)-->
<!-- badges: end -->

rtilities2 provide a set of utilities and RStudio addins for developing R packages.

**Author:** [Ludvig R. Olsen](http://ludvigolsen.dk/) ( r-pkgs@ludvigolsen.dk ) <br/>
**Started:** January 2020 

## Addins

* `Insert Expectations` : generates `testthat` `expect_*` tests from selected code
* `dput() selected` : applies `dput()` to selected code
* `Wrap string with paste0` : splits selected string every n characters and wraps in `paste0` call
* `Insert %>%` 

## Main functions

* `stop_if()`, `warn_if()`, `message_if()`
* `is_between()`
* `%ni%` (read "not in")
* `strip()`

## Installation

```{r eval=FALSE}
devtools::install_github("ludvigolsen/rtilities2")
```

